### 2016-11-22 local-capability-machine.tex
removed old figures
Adjusted scall and call semantics to use explicit register

\begin{description}
\item[\texttt{call} $f(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. An overview of this call:
  \begin{itemize}
  \item Set up activation record
  \item Create local enter capability for activation
  \item Clear unused registers
  \item Jump
  \item Upon return: Run activation code
  \end{itemize}
A more detailed description of each of the above steps:
\begin{description}
  \item [Set up activation record]
    \begin{itemize}
    \item Run malloc to get a piece of memory with space for:
    \begin{itemize}
      \item Words in $\bar{r}_{\var{priv}}$
      \item Code return capability (opc)
      \item Activation code
    \end{itemize}
    \item Store the words in $\bar{r}_{\var{priv}}$ to the activation record. 
    \item Adjust the current pc to point to the return address and save it to the activation record.
    \item Write the activation code to the activation record.
  \end{itemize}
  \item [Create local enter capability for activation] Make the capability for the activation record point to the beginning of the activation record and restrict it to a local-enter capability. Place this capability in $r_0$.
  \item [Clear unused registers]
    Clear all the register that are not $\pcreg$, $r_0$, or in $\bar{r}_{\var{args}}$.
  \item [Jump] jump to $f$
\lau{This needs some thought - how do I jump to $f$. In our semantics, you need a capability in a register in order to do a jump. The only way to still have the $f$ capability in a register is if it is one of the arguments.}
\lau{Maybe instead of having $f$, we use $r_f$ as the register where the ``function'' capability resides.}
  \item [Activation code] The activation code does the following:
    \begin{itemize}
    \item Move the stored ``private'' words in to their respective $\bar{r}_{\var{priv}}$ registers.
    \item Clear all registers but $r_1$, $\pcreg$, and $\bar{r}_{\var{priv}}$.
    \item Load the return address to $\pcreg$
    \end{itemize}
\end{description}
\item[\texttt{malloc x}] Calls malloc to allocates a piece of memory (of an appropriate size). In the program $\texttt{x}$ will henceforth be used to refer to the capability returned by malloc.
\item[\texttt{hstore x n}] Fetches the capability referred to with \texttt{x} and stores \texttt{n} to it.
\item[\texttt{assert x y}] Fetches \texttt{x} and \texttt{y} and compares them. If they are equal, then execution continues. If they are unequal, then the assertion flag is set to 1 and execution halts.
\end{description}

\subsection{Stack}
Some programs will assume access to a stack which will be in part indicated by the program macros, but also in the correctness lemma. The stack is accessed through a local $\rwlx$-capability. Programs will assume that the stack resides in some register, say $r_{\var{stk}}$.
\begin{description}
\item[\texttt{push r}] Pushes the word in register \texttt{r} to the stack by storing it through the stack capability and increment said capability.\footnote{The stack grows upwards.}
\item[\texttt{pop r}] Pops the top word of the stack by loading it to register $r$, moves 0 to the address, and decrementing the stack pointer.
\item[\texttt{scall} $f(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. This call assumes $r_{\var{stk}}$ contains a stack capability. An overview of this call:
  \begin{itemize}
  \item Push restore code to the stack.
  \item Push ``private'' registers to the stack.
  \item Push return address capability 
  \item Push stack pointer
  \item Create local enter capability for restoration
  \item Restrict stack capability
  \item Clear unused registers
  \item Jump
  \item Upon return: Run restore code
  \item Return address:  Restore ``private'' state
\lau{ Need to clear the returned stack. }
  \end{itemize}
A more detailed description of the above steps:
\begin{description}
  \item [Push restore code to the stack]
    Push the restore code to the stack (described later). This code needs to be on the stack to make sure the stack capability can be restored. We try to keep the restore code on the stack minimal.
  \item [Push ``private'' registers to the stack]
    Push all the words in the registers in  $\bar{r}_{\var{priv}}$ to the stack.
  \item [Push return address capability]
    Push a capability for the return address (on the heap) to the stack.
  \item [Push stack pointer]
    Push the full stackpointer to the heap.
  \item [Create local enter capability for restoration]
    Make a new version of the stack pointer that points to the beginning of the restoration code. Restrict it to a local-enter capability and put it in $r_0$.
  \item [Restrict stack capability]
    Make the stack capability only govern the unused part.
  \item [Clear unused registers]
    Clear all registers but $\pcreg$, $r_0$, $r_{\var{stk}}$, and $\bar{r}_{\var{args}}$.
  \item [Jump] Jump to $f$.
\lau{same issue as with \texttt{call}, where dos $f$ come from.}
  \item [Restore code]
    Load the stack capability to $r_{\var{stk}}$. Pop the old program counter to $\pcreg$.
  \item [Return address: Restore ``private'' state]
    \begin{itemize}
    \item Pop the private state on the stack into their respective $\bar{r}_{\var{priv}}$ registers.
    \item Pop the restore code of the stack
    \end{itemize}
\end{description}
\end{description}

\begin{figure}
  \label{fig:stack-before-call}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Heap} \\
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}} \rightarrow$   & local stack\\
   & $\vdots$
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}$\\
\cline{2-2}
$r_0$  & $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,1}$\\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{Stack and register-file before the call}
\end{figure}

\begin{figure}
  \label{fig:stack-after-push}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Heap} \\
   & \\
   & $\vdots$\\
\cline{2-2}
$c_{\var{stk}}' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
   & Restore code \\
\cline{2-2}
   & local stack\\
   & $\vdots$
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}''$\\
\cline{2-2}
$r_0$  & $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}'$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,1}$\\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{Stack and register-file after everything has been pushed to the stack.}
\end{figure}

\begin{figure}
  \label{fig:stack-after-restrict-and-zero}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Heap} \\
   & \\
   & $\vdots$\\
\cline{2-2}
$c_{\var{stk}}'' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
$c_0' \rightarrow$   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}^{(3)}$\\
\cline{2-2}
$r_0$  & $c_0'$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}''$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,1}$\\
\cline{2-2}
$r_{\var{priv},1}$ & 0\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & 0 \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file after the $c_{\var{stk}}'$ has been limited to only give authority over the empty part of the stack (the new capability is $c_{\var{stk}}''$. $c_0'$ is made from $c_{\var{stk}}'$ by setting it to point to the restore code and restricting it to a local enter-capability. }
\end{figure}

\begin{figure}
  \label{fig:stack-upon-return}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Heap} \\
   & \\
   & $\vdots$\\
\cline{2-2} 
   & $?$\\
\cline{2-2} 
$c_{\var{stk}}' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
$c_0' \rightarrow$   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_0'$\\
\cline{2-2}
$r_0$  &  ? \\
\cline{2-2}
$r_{\var{stk}}$  & ? \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & ?\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & ? \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file upon return. }
\end{figure}

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Heap} \\
   & \\
   & $\vdots$\\
\cline{2-2} 
   & $?$\\
\cline{2-2} 
   & 0 \\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}}^{(3)} \rightarrow$  & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
$c_0' \rightarrow$   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc'$\\
\cline{2-2}
$r_0$  &  ? \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}^{(3)}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & ?\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & ? \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file upon return. }
\end{figure}

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Heap} \\
   & \\
   & $\vdots$\\
\cline{2-2} 
   & $?$\\
\cline{2-2} 
   & 0 \\
\cline{2-2}
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}}^{(4)} \rightarrow$   & local stack\\
   & $\vdots$
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc^{(3)}$\\
\cline{2-2}
$r_0$  &  $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}^{(4)}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file upon return. }
\end{figure}

\begin{comment}
\begin{figure}
  \centering
  \begin{tabular}[!h]{r | >{\centering\arraybackslash}p{3cm} |}
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$r_{\var{stk}} \rightarrow$     & Stack cap\\
\cline{2-2}
   & $r_0$-continuation\\
\cline{2-2}
   & o-$\pcreg$\\
\cline{2-2}
   & Restore code\\
   & $\vdots$\\
\cline{2-2}
   & local state\\
   & $\vdots$
\end{tabular}
\caption{Stack after everything stored}
\end{figure}

\begin{figure}
  \centering
  \begin{tabular}[!h]{r | >{\centering\arraybackslash}p{3cm} |}
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$r_{\var{stk}} \rightarrow$      & arg1 \\
\cline{2-2}
   & $\vdots$\\
\cline{2-2}
   & argn \\
\cline{2-2}
   & Stack cap\\
\cline{2-2}
   & $r_0$-continuation\\
\cline{2-2}
   & o-$\pcreg$\\
\cline{2-2}
   & Restore code\\
   & $\vdots$\\
\cline{2-2}
   & local state\\
   & $\vdots$
\end{tabular}
\caption{Stack after arguments pushed to stack an ready to jump}
\end{figure}

\begin{figure}
  \centering
  \begin{tabular}[!h]{r|>{\centering\arraybackslash}p{3cm}|l}
   & &\\
   & $\vdots$ &\\
\cline{2-2}
   & 0 &\\
\cline{2-2}
$r_{\var{stk}} \rightarrow$      & arg1 & \\
\cline{2-2}
   & $\vdots$ & \\
\cline{2-2}
   & argn & \\
\cline{2-2}
   & Stack cap & \\
\cline{2-2}
   & $r_0$-continuation &  \\
\cline{2-2}
   & o-$\pcreg$ & \\
\cline{2-2}
   & Restore code & \rdelim\}{2}{2cm}[variable length]\\
   & $\smash{\vdots}$ & \\
\cline{2-2}
   & & \\
\cline{2-2}
   & local state & \\
   & $\smash{\vdots}$ &
\end{tabular}
\caption{Stack after arguments pushed to stack an ready to jump}
\end{figure}

\begin{figure}
  \centering
  \begin{tabular}[!h]{r | >{\centering\arraybackslash}p{3cm} |}
   & \\
   & $\vdots$\\
\cline{2-2}
   & ? \\
\cline{2-2}
   & Stack cap\\
\cline{2-2}
   & $r_0$-continuation\\
\cline{2-2}
   & o-$\pcreg$\\
\cline{2-2}
$\pcreg \rightarrow$   & Restore code\\
   & $\vdots$\\
\cline{2-2}
   & local state\\
   & $\vdots$
\end{tabular}
\caption{Stack just after return}
\end{figure}

\begin{figure}
  \label{fig:stack-after-call}
  \centering
  \begin{tabular}[!h]{r | >{\centering\arraybackslash}p{3cm} |}
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$r_{\var{stk}} \rightarrow$   & local state\\
   & $\vdots$
\end{tabular}
\caption{Stack after everything has been restored}
\end{figure}
\end{comment}
\subsection{Labels}
\texttt{l:} is a meta level label that can be used to refer to a specific address.

>>>>

\begin{description}
\item[\texttt{call} $r_f(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. An overview of this call:
  \begin{itemize}
  \item Set up activation record
  \item Create local enter capability for activation
  \item Clear unused registers
  \item Jump
  \item Upon return: Run activation code
  \end{itemize}
A more detailed description of each of the above steps:
\begin{description}
  \item [Set up activation record]
    \begin{itemize}
    \item Run malloc to get a piece of memory with space for:
    \begin{itemize}
      \item Words in $\bar{r}_{\var{priv}}$
      \item Code return capability (opc)
      \item Activation code
    \end{itemize}
    \item Store the words in $\bar{r}_{\var{priv}}$ to the activation record. 
    \item Adjust the current pc to point to the return address and save it to the activation record.
    \item Write the activation code to the activation record.
  \end{itemize}
  \item [Create local enter capability for activation] Make the capability for the activation record point to the beginning of the activation record and restrict it to a local-enter capability. Place this capability in $r_0$.
  \item [Clear unused registers]
    Clear all the register that are not $\pcreg$, $r_0$, $r_f$ or in $\bar{r}_{\var{args}}$.
  \item [Jump] jump to $r_f$
  \item [Activation code] The activation code does the following:
    \begin{itemize}
    \item Move the stored ``private'' words in to their respective $\bar{r}_{\var{priv}}$ registers.
    \item Clear all registers but $r_1$, $\pcreg$, and $\bar{r}_{\var{priv}}$.
    \item Load the return address to $\pcreg$
    \end{itemize}
\end{description}
\item[\texttt{malloc x}] Calls malloc to allocates a piece of memory (of an appropriate size). In the program $\texttt{x}$ will henceforth be used to refer to the capability returned by malloc.
\item[\texttt{hstore x n}] Fetches the capability referred to with \texttt{x} and stores \texttt{n} to it.
\item[\texttt{assert x y}] Fetches \texttt{x} and \texttt{y} and compares them. If they are equal, then execution continues. If they are unequal, then the assertion flag is set to 1 and execution halts.
\end{description}

\subsection{Stack}
Some programs will assume access to a stack which will be in part indicated by the program macros, but also in the correctness lemma. The stack is accessed through a local $\rwlx$-capability. Programs will assume that the stack resides in some register, say $r_{\var{stk}}$.
\begin{description}
\item[\texttt{push r}] Pushes the word in register \texttt{r} to the stack by storing it through the stack capability and increment said capability.\footnote{The stack grows upwards.}
\item[\texttt{pop r}] Pops the top word of the stack by loading it to register $r$, moves 0 to the address, and decrementing the stack pointer.
\item[\texttt{scall} $r_f(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. This call assumes $r_{\var{stk}}$ contains a stack capability. An overview of this call:
  \begin{itemize}
  \item Push restore code to the stack.
  \item Push ``private'' registers to the stack.
  \item Push return address capability 
  \item Push stack pointer
  \item Create local enter capability for restoration
  \item Restrict stack capability
  \item Clear unused registers
  \item Jump
  \item Upon return: Run restore code
  \item Return address: Clear the stack segment we gave control over
  \item Restore ``private'' state
  \end{itemize}
A more detailed description of the above steps:
\begin{description}
  \item [Push restore code to the stack]
    Push the restore code to the stack (described later). This code needs to be on the stack to make sure the stack capability can be restored. We try to keep the restore code on the stack minimal.
  \item [Push ``private'' registers to the stack]
    Push all the words in the registers in  $\bar{r}_{\var{priv}}$ to the stack.
  \item [Push return address capability]
    Push a capability for the return address (on the heap) to the stack.
  \item [Push stack pointer]
    Push the full stackpointer to the heap.
  \item [Create local enter capability for restoration]
    Make a new version of the stack pointer that points to the beginning of the restoration code. Restrict it to a local-enter capability and put it in $r_0$.
  \item [Restrict stack capability]
    Make the stack capability only govern the unused part.
  \item [Clear unused registers]
    Clear all registers but $\pcreg$, $r_0$, $r_{\var{stk}}$, and $\bar{r}_{\var{args}}$.
  \item [Jump] Jump to $f$.
\lau{same issue as with \texttt{call}, where dos $f$ come from.}
  \item [Restore code]
    Load the stack capability to $r_{\var{stk}}$. Pop the old program counter to $\pcreg$.
  \item [Return Address:] \forcenewline
    \begin{description}
    \item [Clear the stack segment we gave control over]
    \item [Restore ``private'' state] \forcenewline
      \begin{itemize}
      \item Pop the private state on the stack into their respective $\bar{r}_{\var{priv}}$ registers.
      \item Pop the restore code of the stack
      \end{itemize}
  \end{description}
\end{description}
\end{description}

\begin{figure}
  \label{fig:stack-before-call}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}} \rightarrow$   & local stack\\
   & $\vdots$
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}$\\
\cline{2-2}
$r_0$  & $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}$ \\
\cline{2-2}
$r_f$ & $c_f$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,1}$\\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{Stack and register-file before the call}
\end{figure}

\begin{figure}
  \label{fig:stack-after-push}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
$c_{\var{stk}}' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
   & Restore code \\
\cline{2-2}
   & local stack\\
   & $\vdots$ \\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}''$\\
\cline{2-2}
$r_0$  & $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}'$ \\
\cline{2-2}
$r_f$ & $c_f$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,1}$\\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{Stack and register-file after everything has been pushed to the stack.}
\end{figure}

\begin{figure}
  \label{fig:stack-after-restrict-and-zero}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
$c_{\var{stk}}'' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
$c_0' \rightarrow$   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}^{(3)}$\\
\cline{2-2}
$r_0$  & $c_0'$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}''$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,1}$\\
\cline{2-2}
$r_{\var{priv},1}$ & 0\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & 0 \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file after the $c_{\var{stk}}'$ has been limited to only give authority over the empty part of the stack (the new capability is $c_{\var{stk}}''$. $c_0'$ is made from $c_{\var{stk}}'$ by setting it to point to the restore code and restricting it to a local enter-capability. }
\end{figure}

\begin{figure}
  \label{fig:stack-upon-return}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2} 
   & $?$\\
\cline{2-2} 
$c_{\var{stk}}' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
$c_0' \rightarrow$   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_0'$\\
\cline{2-2}
$r_0$  &  ? \\
\cline{2-2}
$r_{\var{stk}}$  & ? \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & ?\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & ? \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file upon return. }
\end{figure}

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}}^{(3)} \rightarrow$  & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc'$\\
\cline{2-2}
$r_0$  &  ? \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}^{(3)}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & ?\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & ? \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file after clearing stack. }
\end{figure}

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}}^{(4)} \rightarrow$   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc^{(3)}$\\
\cline{2-2}
$r_0$  &  $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}^{(4)}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file upon return. }
\end{figure}

\subsection{Labels}
\texttt{l:} is a meta level label that can be used to refer to a specific address.
